Pool Model

### 2023-12-20 pool_model.tex
nicely format table and include all parameters for the model
put everything from additional file into main file

\documentclass[10pt,A4paper]{article}
\usepackage[
    a4paper,
    inner=2.5cm,
    outer=3cm
]{geometry}
\input{additional_tex/packages}

@@

\subsubsection{Physical Mechanics}

@@

@@

    \begin{tabularx}{\textwidth}{@{}l *5{>{\centering\arraybackslash}X}@{}}

@@

        \cmidrule[1pt](l{\tabcolsep}r{\tabcolsep}){1-3}
        \cmidrule[1pt](l{\tabcolsep}r{\tabcolsep}){4-6}
         & \textbf{Symbol} & \textbf{Value} && \textbf{Symbol} & \textbf{Value}\\

@@

        & Production                & $b$           & $0.1$\unit{\per\minute}\\
        & Inhibition                & $\nu_I$       & $0.1$\unit{\micro\metre\cubed\per\mol}\\
        \textbf{Initial Values}\\

@@

        &                           &               & 0\\

@@

        &                           &               & 0\\
        Relative nutrients          & $R$           & $1.0$
        & Nutrients                 & $A$           & $1.0$\unit{\mol\per\micro\metre\cubed}\\
        Volume inhibitor            & $I$           & $0.0$\unit{\micro\metre\cubed}
        & Inhibitor                 &               & $0.0$\unit{\mol\per\micro\metre\cubed}\\

>>>>

\documentclass[10pt,A4paper]{article}
\usepackage[
    a4paper,
    inner=2.5cm,
    outer=3cm
]{geometry}

\usepackage[utf8]{inputenc}
\usepackage[a4paper,
            inner=2.5cm,
            outer=3cm
            ]{geometry}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off, font=small]{caption}            
\usepackage{acronym}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{hyperref}
\usepackage[backend=biber,
            sorting=none,
%            citestyle=numeric-comp,
%\            bibstyle=ieee, 
            style=numeric-comp,
            hyperref=true,
            maxnames=2,
            url=false,
            isbn=false,
            eprint=false,
            date=year,
            doi=false,
            giveninits=true
            ]{biblatex}
\addbibresource{Bacteria Modelling.bib}
\usepackage{xpatch}
\xpatchbibmacro{journal+issuetitle}{%
\usebibmacro{journal}%
\setunit*{\addspace}%
}{%
\usebibmacro{journal}%
\setunit*{\addcomma\space}%
}{}{}

\renewbibmacro*{name:andothers}{% Based on name:andothers from biblatex.def
  \ifboolexpr{
    test {\ifnumequal{\value{listcount}}{\value{liststop}}}
    and
    test \ifmorenames
  }
    {\ifnumgreater{\value{liststop}}{1}
       {\finalandcomma}
       {}%
     \andothersdelim\bibstring[\emph]{andothers}}
    {}}

%\DeclareFieldFormat[article]{title}{#1}
\DeclareFieldFormat[article]{volume}{\textbf{#1}}
%\DeclareFieldFormat[book]{volume}{\textbf{#1}}

\renewcommand\newunitpunct{\addcomma\space}
\DefineBibliographyStrings{english}{%
page = {},
pages = {},
}

\renewbibmacro{in:}{\addcomma\addspace}

\renewbibmacro*{volume+number+eid}{%
\isdot
\printfield{volume}%
\setunit*{\addcomma\addspace}%
\iffieldundef{number}{}{%
\printtext{no\adddot\addnbthinspace}%
}%
\printfield{number}%
\setunit{\addcomma\space}%
\printfield{eid}}

\setlength{\tabcolsep}{1.3pt}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage[T1]{fontenc}
\usepackage{diagbox}
\usepackage{here}
\usepackage[dvipsnames]{xcolor}
\usepackage{lipsum}
\usepackage{multirow}
\usepackage{ctable} % for \specialrule command
\usepackage{array,booktabs}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\usepackage{subcaption}
\usepackage{float}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{listings-rust}
\lstset{
    language=Rust,
    showstringspaces=false
}
\usepackage{newfloat}
\DeclareFloatingEnvironment[
  name=Listing,
  listname=List of Listings,
  within=section,
]{listing}
\restylefloat{table}
\numberwithin{equation}{section}

\newcommand{\beginsupplement}{%
  \setcounter{subsection}{0}
  \renewcommand{\thesubsection}{S\arabic{subsection}}
  \setcounter{table}{0}
  \renewcommand{\thetable}{S\arabic{table}}%
  \setcounter{figure}{0}
  \renewcommand{\thefigure}{S\arabic{figure}}%
  \setcounter{listing}{0}
  \renewcommand{\thelisting}{S\arabic{listing}}
}

\newcommand{\mbP}{\textbf{P: }}
\newcommand{\mbC}{\textbf{C: }}
\newcommand{\mbx}{\mathbf{x}}
\newcommand{\mbm}{\mathbf{m}}
\newcommand{\mbp}{\mathbf{p}}
\newcommand{\mbu}{\mathbf{u}}
\newcommand{\mbF}{\mathbf{F}}
\newcommand{\mbH}{\mathbf{H}}
\newcommand{\cmtb}[1]{\textcolor{blue} {#1}}
\newcommand{\cmt}[1]{\textcolor{red} {[#1]}}
\newcommand{\etal}{{\textit{et al. }}}

\newacro{ode}[ODE]{Ordinary Differential Equation}
\newacro{glv}[gLV]{generalized Lotka-Volterra}
\newacro{abm}[ABM]{Agent-Based Model}

% Define new style for json listings
% Copied from https://www.latex4technics.com/?note=3QTU
\colorlet{punct}{red!60!black}
\definecolor{background}{HTML}{EEEEEE}
\definecolor{delim}{RGB}{20,105,176}
\colorlet{numb}{magenta!60!black}

\lstdefinelanguage{json}{
    basicstyle=\normalfont\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{background},
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}
      {]}{{{\color{delim}{]}}}}{1},
}

@@

\subsubsection{Physical Mechanics \& Interactions}

@@

The underlying equation of motion is that of a standard damped particle
    m \ddot{\vec{x}} = -\eta\dot{\vec{x}} + \vec{F}

@@

    \begin{tabularx}{\textwidth}{@{}l *2{>{\centering\arraybackslash}X} l *2{>{\centering\arraybackslash}X}@{}}

@@

        \multicolumn{6}{c}{\textbf{Cellular Reactions}}\\
        & Production $I$            & $b$           & $0.1$\unit{\per\minute}\\
        &                           & $\nu_I$       & $0.1$\unit{\micro\metre\cubed\per\mol}\\
        &&
        & Conversion                & $\sigma$      & $0.1$\unit{\micro\metre\cubed\per\mol}\\
        \multicolumn{6}{c}{\textbf{Physical Mechanics \& Interactions}}\\
        &&& Damping                 & $\eta$        & $0.5$\unit{\per\minute}\\
        &&& Mass                    & $m$           & $7.70$\unit{\pico\gram}\\
        &&& Potential               & $\epsilon$    & $0.5$\unit{\pico\gram\micro\metre\per\minute\squared}\\
        \multicolumn{6}{c}{\textbf{Cell Cycle}}\\

@@

        &&& Division Vol.           & $V_t$         & $14.14$\unit{\micro\metre\cubed}\\
        \multicolumn{6}{c}{\textbf{Initial Values}}\\

@@

        & Cell Volume               & $V_{c,A}$     & $7.07$\unit{\micro\metre\cubed}\\

@@

        & Cell Volume               & $V_{c,B}$     & $7.07$\unit{\micro\metre\cubed}\\
        Relative Nutrients          & $R^*$         & $1.0$
        & Nutrients                 & $[R_0]$       & $1.0$\unit{\mol\per\micro\metre\cubed}\\
        Inhibitor                   & $I_0$         & $0.0$\unit{\mol}
        & Inhibitor                 & $[I_0]$       & $0.0$\unit{\mol\per\micro\metre\cubed}\\
